Data preparation for employee category analysis

### 2023-04-24 04. Analysis/scripts/02_data_preparation_clusters_employee.Rmd
Update 02_data_preparation_clusters_employee.Rmd
Developing code to calculate team mode

>>>>

#### Modal size of team over observation window

Calculate number of team members per day by supervisor email.

```{r}
prep_a <- 
  cohort_panel %>% 
  group_by(date,supervisor_e_mail_address) %>% 
  summarise(team_size = n_distinct(person_id)) %>% 
  ungroup()
```

```{r}
prep_a %>% 
  skim()
```

Join to `cohort_panel` only selecting, `person_id`, `date`, and `supervisor_e_mail_address`.

```{r}
prep_b <- 
  cohort_panel %>% 
  select(date,person_id,supervisor_e_mail_address) %>% 
  left_join(prep_a)
```

```{r}
prep_b %>% 
  skim()
```

#### Proportion of working days co-located with at least one other team member
#### Proportion of working days co-located with supervisor
#### Proportion of working days co-located with entire team
#### Proportion of working days entire team is remote
